\documentclass[12pt]{letter}
\usepackage[britdate]{UH-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
% \usepackage[margin=10pt,font=small,labelfont=bf]{caption}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\position{Postdoctoral fellow}
\department{Department of Agricultural Sciences}
\location{University of Helsinki}
\cityzip{Helsinki, Finland}
\telephone{}
\fax{}
\email{alyssa.cirtwill@helsinki.fi}
\url{http://cirtwill.github.io}
\name{Dr. Alyssa R. Cirtwill}


\begin{document}

\begin{letter}{\bf
Prof.~Barrett\\
Editor-in-Chief\\
Proceedings of the Royal Society B} % Name/title of the addressee


\opening{Dear Prof. Barrett,}

We appreciate the opportunity to provide a revision of our manuscript ``Species motif participation provides unique information about species risk of extinction'' for publication in \emph{Proceedings of the Royal Society B}. 
The feedback by the Associate Editor and two external Reviewers was insightful and, we feel, has strengthened our manuscript.
We respond in detail to all comments in a separate response letter (attached).


Please note that the initial corresponding author, Anna \r{A}kesson, is leaving academia and will have limited ability to respond to any reader queries.
We have therefore, with the consent of all concerned, changed corresponding authorship to the other joint first author, Alyssa Cirtwill.
At the same time, we have reordered these joint first authors so that the corresponding author continues to appear first.
We hope that this change does not create any administrative issues.


We thank you once again for the helpful comments on our previous revision and for the opportunity to submit a revision.

On behalf of Anna {\AA}kesson, Kate Wootton, and Anna Ekl\"of,

\closing{Sincerely,}
\vspace{4\parskip}
\centering


\end{letter} 
\end{document}

